Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)

### 2015-09-16 research_class/paper.tex
Fix article: "an X"
Not sure: formalize with s/basically/essentially/
I'm not sure this is more formal, but "basically" struck me as being a bit
informal.

Automated testing of the Raft over WebRTC system was performed by
leveraging the SlimerJS scriptable browser environment. SlimerJS
enables web applications to be scripted by loading pages in a special
Mozilla rendering environment called XULRunner. The XULRunner instance
is directed to a X virtual frame buffer (xvfb) which provides
effectively headless testing.

@@

Writing tests using SlimerJS involves creating JavaScript programs
that are run within the SlimerJS environment. These scripts can create
browser instances (basically headless browser tabs), query the status
of those pages and execute JavaScript within the context of the pages
themselves.

>>>>

Automated testing of the Raft over WebRTC system was performed by
leveraging the SlimerJS scriptable browser environment. SlimerJS
enables web applications to be scripted by loading pages in a special
Mozilla rendering environment called XULRunner. The XULRunner instance
is directed to an X virtual frame buffer (xvfb) which provides
effectively headless testing.

@@

Writing tests using SlimerJS involves creating JavaScript programs
that are run within the SlimerJS environment. These scripts can create
browser instances (essentially headless browser tabs), query the status
of those pages and execute JavaScript within the context of the pages
themselves.
